---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# South Carolina

We will subset the data by sex to see if the drug is sex specific.

Results

Graphical Results 

Drug vs. Sex barchart(South Carolina): 

```{r}
barchartGC(~group+sex, data = Scarolina, type = "percent", main = "Drug vs. Sex (Scarolina)")
```

After looking at the graphical data, males and females are equal whether they took the drug or took the placebo. 

Numerical Results

The rowPerc function from tigerstats will be used to create a two-way table to look at the data numerically.

Drug vs. Sex two-way table (South Carolina):

```{r}
data(Scarolina)
SouthCarolina <- xtabs(~group+sex, data = Scarolina)
rowPerc(SouthCarolina)
```

Of those in the drug group, 50% were male and 50% were female.
Of those in the placebo group, 50% were male and 50% were female. 

Inferential Results 



# Central Africa

We will subset the data by sex to see if the drug is sex specific.



# Korea

We will subset the data by sex to see if the drug is sex specific.






