---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
source("MakeData.R")
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# South Carolina

We will subset the data by sex to see if the drug is sex specific.

Results

Graphical Results 

Infected vs. Group barchart(South Carolina): 

```{r}
ScarolinaM_table <- xtabs(~infected+group, data = ScarolinaM)
barchartGC(ScarolinaM_table, type = "percent", main = "Infected vs. Group (Male)")
ScarolinaF_table <- xtabs(~infected+group, data = ScarolinaF)
barchartGC(ScarolinaF_table, type = "percent", main = "Infected vs. Group (Female)")
```

 There seems to be a relationship between sex and the effectiveness of the drug. Males are more likely to acquire aids while on the drug. They are about evenly distributed when it comes to not acquiring aids whether they are taking the drug or the placebo. Females are more likely to acquire aids while on the placebo. They are also evenly distributed when it comes to not being infected when they are taking the drug or placebo. 

Numerical Results

The rowPerc function from tigerstats will be used to create a two-way table to look at the data numerically.

Infected vs. Group two-way table (South Carolina):

```{r}
ScarolinaM_table <- xtabs(~infected+group, data = ScarolinaM)
rowPerc(ScarolinaM_table)
ScarolinaF_table <- xtabs(~infected+group, data = ScarolinaF)
rowPerc(ScarolinaF_table)
```

Of those in the aids male group, 57.35% had aids while taking the drug, 42.65% had aids while taking the placebo. 
Of those in the none male group, 49.52% were not infected while taking the drug, 50.48% were not infected while taking the placebo. 
Of those in the aids female group, 38.83% had aids while taking the drug, 61.17% had aids while taking the placebo. 
Of those in the none female group, 50.55% were not infected while taking the drug, 49.45% were not infected while taking the placebo. 

Inferential Results 

Now the chisqtestGC function from tigerstats will be used to run the two chi-square tests. Both tests will be runned with the assumption that there is no relationship between sex and the effectiveness of the drug. 

 Scarolina Infected vs. Group chi-square test: 
 
 H0: The effectiveness of the drug is independant of sex. 
 
 Ha: The effectivness of the drug and sex are related. 

```{r}
chisqtestGC(ScarolinaM_table)
```

Our P-value is 0.0926. This means the probability of getting a sample like this under these conditions when the null hypothesis is true is about nine percent. This is above the threshold which is typically five percent. since the P-value is high, we will fail to reject the null hypothesis and conclude that there is no relationship between sex and the effectiveness of the drug. 

```{r}
chisqtestGC(ScarolinaF_table)
```

The P-value is 0.0264. This means the probability of getting sample under these conditions when the null hypothesis is true, is about two percent. This is below the threshold which is typically five percent. Since the P-value is too low, we will reject the null hypothesis and conclude that there is a relationship between sex and the effectiveness of the drug. 

# Central Africa

We will subset the data by sex to see if the drug is sex specific.



# Korea

We will subset the data by sex to see if the drug is sex specific.






